Building Large-Scale Cross-lingual Knowledge Base from Multi-Encyclopedia

### 2015-05-28 nlpcc/paper.tex
1

\subsubsection{Infobox-properties}
Attributes acquired from infobox are considered as Infobox-properties, such as 上映时间(release date), 导演(directed by) in a movie's infobox. All attributes relate with a typical value in the infobox. The value maybe a text or a reference to another entity. The type of a property, datatype or object, depends on the value. Ordinarily, a plain text value marks the property as datatype while an entity reference determines the property as object. For example, the attribute 上映时间(release date) can be defined as a datatype property as its value is a datetime string. Meanwhile, 导演(directed by) can be an object property because its value points to a person who directed the movie.

We occur some challenges when extracting properties from infoboxes:
\begin{itemize}
    \item The attribute label displayed in webpage infobox is inconsistent with it in dump file of Wikipedia. Fig.\ref{fig:infobox-template} gives a mapping result of display label and dump label in \emph{Interstellar}' infobox. The left is infobox while the other is a snap from dump file in Wikipedia. This movie's infobox follows template \emph{Infobox film}, where dump labels come from. Obviously the two labels are similar but not the same. As the property labels from Hudong Baike and Baidu Baike are equal to text displayed on the webpage, we have to explore the display labels in Wikipedia rather than dump labels extracted from data file.
    \begin{figure}[ht]
        \centerline{\includegraphics[width=1\columnwidth]{fig/infobox-template}}
        \label{fig:infobox-template}
        \caption{Comparison of display label and dump label in \emph{Interstellar} infobox}
    \end{figure}%
    \item There are special characters in labels. For example, Wikipedia usually use hyphen "-" or dot "•" to mark sublabels. Population property have sub-properties of "Density" and "Urban". In addition, odd signs, such as colon or asterisk, may occur in Baidu or Hudong property labels by mistake.
\end{itemize}

@@

However, due to following templates, Infobox-properties have no obvious cross-lingual links. To acquire such links, we go through the following steps: (1) Given a matched template, that is a template has infobox rules in both English and Chinese, find the mapping pairs; (2) Given the English and Chinese infoboxes of a matched instance, compare the templates they use, find the matched label mapping to the same dump label. (3) Given the English and Chinese infoboxes of a matched instance, to datatype properties, compare the similarity of literal value; to object properties, check whether the value refer to the same entity. The whole process can be summarized as Algorithm \ref{alg:ple}. Some of the symbols have already denoted in \ref{sed:definition}
\subsection{Cross-lingual Linking}
In order to make the ontology of one encyclopedia link to others, we unify the same concept, instance and property from four source to unique one and make identifier. For example, we merge instances by the following method:

\begin{enumerate}[1)]
    \item Given an instance extracted from Chinese Wikipedia, find the entity in Hudong and Baidu Baike with the same title.
    \item Given an instance extracted from Hudong, find the entity which is not in Chinese Wikipedia but in BaiduBaike with the same title.
    \item The other instances existing in only one encyclopedia are considered as an independent instance. Up to now, we have combined all Chinese articles describing the same entity as one instance. Each instance may correspond to 1 to 3 sources.
    \item To a $L_{z}(a)$, which is same as $Ti(a)$, find whether there is an English cross-lingual link in $CL<L_{e}, L_{z}>$. If exists, make the two as one instance and identify it using an ID.
    \item If a $L_{z}$ or a $L_{e}$ has no matched cross-lingual link, number it with an independent ID.
\end{enumerate}

>>>>

\subsubsection{Infobox-properties}
Attributes acquired from infobox are considered as Infobox-properties, such as 上映时间(release date), 导演(directed by) in a movie's infobox. Each attribute in the infobox is related to its own corresponding value. The value maybe a text or a reference to another entity. The type of a property, datatype or object, depends on the type of the value. Ordinarily, a plain text value marks the property as datatype while an entity reference determines the property as objecttype. For example, the attribute 上映时间(release date) can be defined as a datatype property as its value is a datetime string. Meanwhile, 导演(directed by) can be an object property because its value points to a person who directed the movie.

We are challenged when extracting properties from infoboxes:
\begin{itemize}
    \item The attribute label displayed in the webpage infobox is inconsistent with it in the published dump file of Wikipedia. Fig.\ref{fig:infobox-template} gives a mapping result of display label and dump label in \emph{Interstellar}' infobox. The left is infobox while the other is a snap from dump file in Wikipedia. This movie's infobox follows template \emph{Infobox film}, where dump labels come from. Obviously the two labels are similar but not the same. As a result we have to explore the display labels in Wikipedia rather than dump labels extracted from data file. As to Chinese sources, the property labels from Hudong Baike and Baidu Baike are equal literally to texts displayed on the webpage, so we don't need extra process as we have in Wikipedia.
    \begin{figure}[ht]
        \centerline{\includegraphics[width=1\columnwidth]{fig/infobox-template}}
        \label{fig:infobox-template}
        \caption{Comparison of display label and dump label in \emph{Interstellar} infobox}
    \end{figure}%
    \item There are special characters in labels. For example, Wikipedia usually use hyphen "-" or dot "•" to mark sublabels. For example, population property have sub-properties "-Density" and "-Urban". In addition, odd signs, such as colon or asterisk, may occur in Baidu or Hudong property labels by mistake.
\end{itemize}

@@

However, due to following templates, Infobox-properties have no obvious cross-lingual links. To acquire such links, we take the following steps: (1) Given a matched template, which is a template having infobox rules in both English and Chinese, find the mapping pairs; (2) Given the English and Chinese infoboxes of a matched instance, compare the templates they use, find the matched label mapping to the same dump label. (3) Given the English and Chinese infoboxes of a matched instance, to datatype properties, compare the similarity of literal value; to object properties, check whether the value refer to the same entity. The whole process can be summarized as Algorithm \ref{alg:ple}. Some of the symbols have already denoted in \ref{sed:definition}
\subsection{Cross-lingual Linking}
In order to make the ontology of one encyclopedia link to others, we unify the same concept, instance and property from four source to unique one and make identifier. For example, we merge instances by the following method:

\begin{enumerate}[1)]
    \item Given an instance extracted from Chinese Wikipedia, find the entity in Hudong and Baidu Baike with the same title.
    \item Given an instance extracted from Hudong, find the entity which is not in Chinese Wikipedia but in Baidu Baike with the same title.
    \item Other instances existing in only one encyclopedia are considered as an independent instance. Up to now, we have combined all Chinese articles describing the same entity as one instance. Each instance may correspond to 1 to 3 sources.
    \item To a $L_{z}(a)$, which is same as $Ti(a)$, find whether there is an English cross-lingual link in $CL<L_{e}, L_{z}>$. If exists, make the two as one instance and identify it using an ID.
    \item If a $L_{z}$ or a $L_{e}$ has no matched cross-lingual link, number it with an independent ID.
\end{enumerate}
